\Large Exponential Random Graph Models with Big Networks: Maximum Pseudolikelihood Estimation and the\\Parametric Bootstrap

### 2017-06-25 TeX/paper.tex
Add files via upload

\textbf{continue here}
The nodal attribute that we implement for this network 
 In order to include nodal covariates into the ERGM, the vector of nodal attributes is expanded into an artificial matrix $C$, which has the same dimensions as $G$. The first row of matrix $C$ consists of the first actor's attribute, repeated $N$ times. The second row of matrix $C$, consists of the second actor's attribute, repeated $N$ times, and so on. Then, the statistics for a nodal covariate is defined as

@@

We estimate the coefficient of this matrix using both techniques, the MCMLE and the bootstrapped MPLE. The MCMLE requires a sample size of at least $100000$ networks to converge. The bootstrapped MPLE was estimated by using 500 simulated networks. As we described in the chapter {\it Estimation}, only one edge at a time is changed when simulating networks. For better comparison, we chose the same Burn-In ($163840$ MH-steps) and the same number of iterations ($10240$ MH-steps) for sampling networks. The results can be found in table \ref{sc_results}.\\[0.3cm]

\begin{table}[]
\hspace*{-1.5cm}
\begin{tabular}{|
>{\columncolor[HTML]{EFEFEF}}l |l|l|l|l|l|l|}
\hline
\cellcolor[HTML]{EFEFEF}                   & \multicolumn{2}{c|}{\cellcolor[HTML]{EFEFEF}MCMLE}                   & \multicolumn{2}{c|}{\cellcolor[HTML]{EFEFEF}Logistic Regression}       & \multicolumn{2}{c|}{\cellcolor[HTML]{EFEFEF}bootstrapped MPLE}     \\ \cline{2-7} 
\multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}} & \cellcolor[HTML]{EFEFEF}Estimate & \cellcolor[HTML]{EFEFEF}St. Error & \cellcolor[HTML]{EFEFEF}Estimate & \cellcolor[HTML]{EFEFEF}St. Error & \cellcolor[HTML]{EFEFEF}Lower Bound & \cellcolor[HTML]{EFEFEF}Upper Bound \\ \hline
Edges                                      & -5.657                           & 0.028                             & -4.568                       & 0.038                                    & -5.160 & -4.530  \\ \hline
Nodecov.Salience                           & 0.592                            & 0.012                             &   1.482                               & 0.009                                   & 1.413 & 1.890  \\ \hline
Nodecov.Year                               & 0.253                            & 0.012                             &     0.208                             & 0.015                                   & 0.182 & 0.504  \\ \hline
Absdiff.Year                               & -2.470                           & 0.160                             &  -3.121                                & 0.194                             & -3.308 & -2.434  \\ \hline
Absdiff.Year.Squared                       & 0.221                            & 0.066                             &   0.436                               & 0.080                                   & -0.028 & 0.517  \\ \hline
DSP(0)                                     & 0.0005                           & 0.0002                            &    0.021                              & 0.0002                                   & 0.019 & 0.031  \\ \hline
ESP(0)                                     & -3.129                           & 0.012                             &    -2.162                              & 0.004                                   & -2.179 & -1.511  \\ \hline
\end{tabular}
\caption{Estimation results for the Supreme Court Network using MCMLE, bootstrapped MPLE and logistic regression}
\label{sc_results}
\hspace*{-1cm}
\end{table}

>>>>

As nodal attribute we implement the partisanship of the bill sponsor. In order to include nodal covariates into the ERGM, the vector of nodal attributes is expanded into an artificial matrix $C$, which has the same dimensions as $G$. The first row of matrix $C$ consists of the first actor's attribute, repeated $N$ times. The second row of matrix $C$, consists of the second actor's attribute, repeated $N$ times, and so on. Then, the statistics for a nodal covariate is defined as

@@

We estimate the coefficient of this matrix using both techniques, the MCMLE and the bootstrapped MPLE. The MCMLE requires a sample size of at least $1000$ networks to converge. The bootstrapped MPLE was estimated by using 500 simulated networks. As we described in the chapter {\it Estimation}, only one edge at a time is changed when simulating networks. For better comparison, we chose the same Burn-In ($300.000$ MH-steps) and the same number of iterations ($30.000$ MH-steps) for sampling networks. The results can be found in table \ref{sc_results}.\\[0.3cm]

\begin{table}[]
%\hspace*{-1.5cm}
\begin{tabular}{|
>{\columncolor[HTML]{EFEFEF}}l |l|l|l|l|l|l|}
\hline
\cellcolor[HTML]{EFEFEF}                   & \multicolumn{2}{c|}{\cellcolor[HTML]{EFEFEF}MCMLE}                   & \multicolumn{2}{c|}{\cellcolor[HTML]{EFEFEF}Logistic Regression}       & \multicolumn{2}{c|}{\cellcolor[HTML]{EFEFEF}bootstrapped MPLE}     \\ \cline{2-7} 
\multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}} & \cellcolor[HTML]{EFEFEF}Estimate & \cellcolor[HTML]{EFEFEF}St. Error & \cellcolor[HTML]{EFEFEF}Estimate & \cellcolor[HTML]{EFEFEF}St. Error & \cellcolor[HTML]{EFEFEF}Lower Bound & \cellcolor[HTML]{EFEFEF}Upper Bound \\ \hline
Edges                                      & -5.657                           & 0.028                             & -4.568                       & 0.038                                    & -5.160 & -4.530  \\ \hline
Spnsor Party                          & 0.592                            & 0.012                             &   1.482                               & 0.009                                   & 1.413 & 1.890  \\ \hline
Alternating k-star                              & 0.253                            & 0.012                             &     0.208                             & 0.015                                   & 0.182 & 0.504  \\ \hline
\end{tabular}
\caption{Estimation results for the Cosponsorship network using MCMLE, logistic regression and bootstrapped MPLE}
\label{sc_results}
%\hspace*{-1cm}
\end{table}
